\sout{Machine Learning for Global Conquest} \\ Multimatrices and Their Derivatives

### 2021-01-05 Math/book.tex
Updating book.

\begin{example}
Lets find all the inverses of $X \mmult{2} A$ where $\shape{A} = <2,2,2,2>$ and
its values are given by this table:
\begin{table}[h!]
\begin{center}
\begin{tabular}{c c c c | c}
$\bar{a}[1]$ & $\bar{a}[2]$ & $\bar{a}[3]$ & $\bar{a}[4]$ & $A[\bar{a}]$ \\
\hline
1           & 1           & 1           & 1           & -1 \\
2           & 1           & 1           & 1           & 2 \\
1           & 2           & 1           & 1           & 0 \\
2           & 2           & 1           & 1           & 0 \\

1           & 1           & 2           & 1           & 1 \\
2           & 1           & 2           & 1           & 0.5 \\
1           & 2           & 2           & 1           & 0 \\
2           & 2           & 2           & 1           & 0 \\

1           & 1           & 1           & 2           & 0 \\
2           & 1           & 1           & 2           & 0 \\
1           & 2           & 1           & 2           & -1 \\
2           & 2           & 1           & 2           & 2 \\

1           & 1           & 2           & 2           & 0 \\
2           & 1           & 2           & 2           & 0 \\
1           & 2           & 2           & 2           & 1 \\
2           & 2           & 2           & 2           & 0.5
\end{tabular}
\end{center}
\end{table}
Then by theorem \ref{inverse_shape} we know that the inverses will be of the form,
$X \mmult{2} A \mmult{2} B$ or $X \mmult{2} A \mmult{1} C$ for multimatrices
$B$ or $C$ if they exist.

Let's try solving $A \mmult{2} B = \Ident^2(\left<2,2\right>)$ first to get $B$.
We can first tell that $\shape{B} = \left<2,2,2,2\right>$ based on the shape of $A$ and
the shape of the RHS.
This problem can then be reshaped to the following 2d problem,

TODO: what the fuck these numbers are wrong.
\[
\left[
  \begin{array}{c c c c}
    -1 & 0 & 2 & 0 \\ 
    0 & -1 & 0 & 2 \\
    1 & 0 & 0.5 & 0 \\
    0 & 1 & 0 & 0.5
  \end{array}
\right]
B' =
\left[
  \begin{array}{c c c c}
    1 & 0 & 0 & 0 \\
    0 & 1 & 0 & 0 \\
    0 & 0 & 1 & 0 \\
    0 & 0 & 0 & 1
  \end{array}
\right]
\]
Which, once solved, yields,
\[
B' =
\left[
  \begin{array}{c c c c}
    -1/5 & 0 & 2/5 & 0 \\
    0 & -1/5 & 0 & 2/5 \\
    4/5 & 0 & 2/5 & 0 \\
    0 & 4/5 & 0 & 2/5
  \end{array}
\right]
\]
Therefore $B$ is,
\begin{table}[h!]
\begin{center}
\begin{tabular}{c c c c | c}
$\bar{b}[1]$ & $\bar{b}[2]$ & $\bar{b}[3]$ & $\bar{b}[4]$ & $B[\bar{b}]$ \\
\hline
1           & 1           & 1           & 1           & -1/5 \\
1           & 1           & 1           & 2           & 0 \\
1           & 1           & 2           & 1           & 2/5 \\
1           & 1           & 2           & 2           & 0 \\
1           & 2           & 1           & 1           & 0 \\
1           & 2           & 1           & 2           & -1/5 \\
1           & 2           & 2           & 1           & 0 \\
1           & 2           & 2           & 2           & 2/5 \\
2           & 1           & 1           & 1           & 4/5 \\
2           & 1           & 1           & 2           & 0 \\
2           & 1           & 2           & 1           & 2/5 \\
2           & 1           & 2           & 2           & 0 \\
2           & 2           & 1           & 1           & 0 \\
2           & 2           & 1           & 2           & 4/5 \\
2           & 2           & 2           & 1           & 0 \\
2           & 2           & 2           & 2           & 2/5 
\end{tabular}
\end{center}
\end{table}

@@

\[
\left[
  \begin{array}{c c}
    -1 & 2 \\
    0 & 0 \\
    1 & 0.5 \\
    0 & 0 \\
    0 & 0 \\
    -1 & 2 \\
    0 & 0 \\
    1 & 0.5
  \end{array}
\right]
C
=
\left[
  \begin{array}{c c}
    1 & 0 \\
    0 & 0 \\
    0 & 1 \\
    0 & 0 \\
    0 & 0 \\
    1 & 0 \\
    0 & 0 \\
    0 & 1
  \end{array}
\right]
\]
And through some miracle (or author fiat) this actually has a solution,
\[
  C =
  \left[
    \begin{array}{c c}
      -1/5 & 4/5 \\
      2/5 & 2/5
    \end{array}
  \right]
\]
\end{example}

>>>>

\begin{example}
Lets find all the inverses of $X \mmult{2} A$ where $\shape{A} = <2,2,2,2>$ and
its values are given by this table:
\begin{table}[h!]
\begin{center}
\begin{tabular}{c c c c | c}
$\bar{a}[1]$ & $\bar{a}[2]$ & $\bar{a}[3]$ & $\bar{a}[4]$ & $A[\bar{a}]$ \\
\hline
1           & 1           & 1           & 1           & -1 \\
2           & 1           & 1           & 1           & 0 \\
1           & 2           & 1           & 1           & 1 \\
2           & 2           & 1           & 1           & 0 \\

1           & 1           & 2           & 1           & 0 \\
2           & 1           & 2           & 1           & -1 \\
1           & 2           & 2           & 1           & 0 \\
2           & 2           & 2           & 1           & 1 \\

1           & 1           & 1           & 2           & 2 \\
2           & 1           & 1           & 2           & 0 \\
1           & 2           & 1           & 2           & 1/2 \\
2           & 2           & 1           & 2           & 0 \\

1           & 1           & 2           & 2           & 0 \\
2           & 1           & 2           & 2           & 2 \\
1           & 2           & 2           & 2           & 0 \\
2           & 2           & 2           & 2           & 1/2
\end{tabular}
\end{center}
\end{table}
Then by theorem \ref{inverse_shape} we know that the inverses will be of the form,
$X \mmult{2} A \mmult{2} B$ or $X \mmult{2} A \mmult{1} C$ for multimatrices
$B$ or $C$ if they exist.

Let's try solving $A \mmult{2} B = \Ident^2(\left<2,2\right>)$ first to get $B$.
We can first tell that $\shape{B} = \left<2,2,2,2\right>$ based on the shape of $A$ and
the shape of the RHS.
This problem can then be reshaped into a problem where $A' \mmult{1} B' = I'$
Where $\shape{A'} = \left<4,4\right>$ is defined like this,

\begin{table}[h!]
\begin{center}
\begin{tabular}{c c | c}
$\bar{a}'[1]$ & $\bar{a}'[2]$ & $A'[\bar{a}']$ \\
\hline
1           & 1           & -1 \\
2           & 1           & 0 \\
3           & 1           & 1 \\
4           & 1           & 0 \\

1           & 2           & 0 \\
2           & 2           & -1 \\
3           & 2           & 0 \\
4           & 2           & 1 \\

1           & 3           & 2 \\
2           & 3           & 0 \\
3           & 3           & 1/2 \\
4           & 3           & 0 \\

1           & 4           & 0 \\
2           & 4           & 2 \\
3           & 4           & 0 \\
4           & 4           & 1/2
\end{tabular}
\end{center}
\end{table}

With $\Ident^2(\left<2,2\right>)$ being reshaped into $I'$ similarly to form this equation,

\[
\left[
  \begin{array}{c c c c}
    -1 & 0 & 2 & 0 \\
    0 & -1 & 0 & 2 \\
    1 & 0 & 1/2 & 0 \\
    0 & 1 & 0 & 1/2 \\
  \end{array}
\right]
B' =
\left[
  \begin{array}{c c c c}
    1 & 0 & 0 & 0 \\
    0 & 1 & 0 & 0 \\
    0 & 0 & 1 & 0 \\
    0 & 0 & 0 & 1
  \end{array}
\right]
\]
Which, once solved, yields,
\[
B' =
\left[
  \begin{array}{c c c c}
    -1/5 & 0 & 4/5 & 0 \\
    0 & -1/5 & 0 & 4/5 \\
    2/5 & 0 & 2/5 & 0 \\ 
    0 & 2/5 & 0 & 2/5
  \end{array}
\right]
\]

Therefore $B$ is as shown in the table below.
\begin{table}[h!]
\begin{center}
\begin{tabular}{c c c c | c}
$\bar{b}[1]$ & $\bar{b}[2]$ & $\bar{b}[3]$ & $\bar{b}[4]$ & $B[\bar{b}]$ \\
\hline
1           & 1           & 1           & 1           & -1/5 \\
2           & 1           & 1           & 1           & 0 \\
1           & 2           & 1           & 1           & 2/5 \\
2           & 2           & 1           & 1           & 0 \\
1           & 1           & 2           & 1           & 0 \\
2           & 1           & 2           & 1           & -1/5 \\
1           & 2           & 2           & 1           & 0 \\
2           & 2           & 2           & 1           & 2/5 \\
1           & 1           & 1           & 2           & 4/5 \\
2           & 1           & 1           & 2           & 0 \\
1           & 2           & 1           & 2           & 2/5 \\
2           & 2           & 1           & 2           & 0 \\
1           & 1           & 2           & 2           & 0 \\
2           & 1           & 2           & 2           & 4/5 \\
1           & 2           & 2           & 2           & 0 \\
2           & 2           & 2           & 2           & 2/5
\end{tabular}
\end{center}
\end{table}

@@

\[
\left[
  \begin{array}{c c}
    -1 & 2 \\
    0 & 0 \\
    1 & 1/2 \\
    0 & 0 \\
    0 & 0 \\
    -1 & 2 \\
    0 & 0 \\
    1 & 1/2 \\
  \end{array}
\right]
C
=
\left[
  \begin{array}{c c}
    1 & 0 \\
    0 & 0 \\
    0 & 1 \\
    0 & 0 \\
    0 & 0 \\
    1 & 0 \\
    0 & 0 \\
    0 & 1
  \end{array}
\right]
\]
And through some miracle (or author fiat) this actually has a solution,
\[
  C =
  \left[
    \begin{array}{c c}
      -1/5 & 4/5 \\
      2/5 & 2/5
    \end{array}
  \right]
\]
\end{example}

TODO: can you turn a smaller inverse multimatrix into a larger inverse?
